On Population-Based FA Analysis with Non-independent Normalization and Statistics

### 2011-06-08 ANTsTBSS/paper.tex
ENH: adding why the paper hasnt been written before sentences

Caveats with our analysis include a lack of ground truth in the
clinical component of the study.   Additionally, we are not addressing
our results' biological plausibility, nor do we
intend to (in this paper) enter into discussion on the mechanisms of
TBI, gender difference and DTI that may lead to the detected results.
Rather, we focus on the technical issue of circularity induced by
normalizing the image feature of interest with functions that maximize
the statistic used in hypothesis testing.  We also cannot argue that our analysis
invalidates previous results that used a circular strategy.  Instead, we encourage the community to
reexamine FA normalization and analysis methods and to consider the
potential confounds highlighted in this paper.  Rank tests
provide a more conservative alternative as does the methodology
presented here based on T1 to DT intrasubject mapping and T1
normalization.

>>>>

Caveats with our analysis include a lack of ground truth in the
clinical component of the study.   Additionally, we are not addressing
our results' biological plausibility, nor do we
intend to (in this paper) enter into discussion on the mechanisms of
TBI, gender difference and DTI that may lead to the detected results.
Rather, we focus on the technical issue of circularity induced by
normalizing the image feature of interest with functions that maximize
the statistic used in hypothesis testing.  We also cannot argue that our analysis
invalidates previous results that used a circular strategy.  Instead, we encourage the community to
reexamine FA normalization and analysis methods and to consider the
potential confounds highlighted in this paper.  Rank tests
provide a more conservative alternative as does the methodology
presented here based on T1 to DT intrasubject mapping and T1
normalization.  To our surprise, we could not find a prior publication that directly
addresses this issue.  Two reasons may be that the majority of
technical work using DTI has focused on more cutting-edge issues while
the clinical work using DTI is more concerned with generating
statistically significant results.  An additional reason may be that
only recently have toolkits emerged to enable easy comparison of
statistical techniques (via {\bf R}), normalization methods (ANTs) and
diffusion tensor processing (Camino).
